sensiAnPaper1All

### 2016-05-24 inst/documents/sensiAnPaper1All.Rmd
test scenarios

  #nScenarios <- 10  
  #nScenarios <- 100
  nScenarios <- 500  
  #nScenarios <- 10000

@@

  ## do model runs
  # listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment )
  # listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment )
  # listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment )

  ## 23/3/16 expt with an 'old' insecticide
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment, old_insecticide=TRUE )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment, old_insecticide=TRUE )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment, old_insecticide=TRUE )

>>>>

  nScenarios <- 10  
  #nScenarios <- 100
  #nScenarios <- 500  
  #nScenarios <- 10000

@@

  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment )

  ## 23/3/16 expt with an 'old' insecticide
  # listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment, old_insecticide=TRUE )
  # listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment, old_insecticide=TRUE )
  # listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment, old_insecticide=TRUE )
